Fast-Match:\\Fast and Robust Feature Matching on Large Images

### 2014-06-19 paper.tex
Corrected mega pixel to megapixel
Minor fixes

%===========================================================
\title{Fast-Match: Fast and robust feature matching on large images}
\titlerunning{ACCV-14 submission ID \ACCV14SubNumber}
\authorrunning{ACCV-14 submission ID \ACCV14SubNumber}

@@

\begin{abstract}
    Both consumer cameras and camera phones produce images that often exceed 10 megapixels. Yet computing and matching local features in images of this size can easily take more than twenty seconds using fast matching algorithms. This is much too slow for interactive applications and much too expensive for large scale image operations. We introduce \emph{Fast-Match}, an algorithm designed to swiftly match large images without compromising on matching precision or recall. \emph{Fast-Match} derives its speed from only computing features in those parts of the image that can be confidently matched. We show that \emph{Fast-Match} is an order of magnitude faster than \emph{Ratio-Match}, yet often doubles the precision on difficult to match image pairs at equal recall. In addition we prove that when one image is known in advance, \emph{Fast-Match} can achieve linear performance $O(n)$ in the number of feature points $n$.
\end{abstract}

@@

\begin{figure}[tb]
    \centering
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-fastmatch}
    \end{subfigure}%
    ~%\vspace{1.5 mm}
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-ratiomatch}
    \end{subfigure}%
    \caption{The 50 best matches by the proposed \emph{Fast-Match} algorithm (left) and the \emph{Ratio-Match} algorithm \cite{lowe2004sift} (right). The lines between the image pairs denote a match as proposed by the algorithm. For \emph{Fast-Match} the zones of the right image where local features were computed has been marked with a blue square.}
    \label{fig:match_example}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.75\columnwidth]{images/exploration}
\caption{Exploration of features based on match. The areas shaded blue are the areas that were searched to obtain the match. The areas shaded green are candidate areas for obtaining more matches.}
\label{fig:exploration}
\end{figure}

@@

@@

    \caption{15 objects from the 3D Objects dataset by Moreels
    and Pietro \cite{moreels2007evaluation}.}
    \label{fig:3d_objects}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth]{images/timings}
    \caption{The duration in seconds of different variations of \emph{Fast-Match} and \emph{Ratio-Match}. The top plot shows results for two 10~MPixel images two 3~Mpixel images is used for the comparison at the bottom. From the left, the first two results presume a precached image while the rest do not require knowing any inputs beforehand. The image pairs used be seen in Figure~\ref{fig:match_example}}
    \label{fig:timings}
\end{figure}

>>>>

%===========================================================
\title{Fast-Match:\\Fast and Robust Feature Matching on Large Images}
\titlerunning{ACCV-14 submission ID \ACCV14SubNumber}
\authorrunning{ACCV-14 submission ID \ACCV14SubNumber}

@@

\begin{abstract}
    Consumer digital cameras and camera phones produce images that often exceed 10 megapixels. Yet computing and matching local features in images of this size can easily take more than twenty seconds using fast matching algorithms. This is much too slow for interactive applications and much too expensive for large scale image operations. We introduce \emph{Fast-Match}, an algorithm designed to swiftly match large images without compromising on matching precision or recall. \emph{Fast-Match} derives its speed from only computing features in those parts of the image that can be confidently matched. We show that \emph{Fast-Match} is an order of magnitude faster than \emph{Ratio-Match}, yet often doubles the precision on difficult to match image pairs at equal recall. In addition we prove that when one image is known in advance, \emph{Fast-Match} can achieve linear performance $O(n)$ in the number of feature points $n$.
\end{abstract}

@@

\begin{figure}[tb]
    \centering
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-fastmatch}
    \end{subfigure}%
    ~%\vspace{1.5 mm}
    \begin{subfigure}[t]{0.5\columnwidth}
        \includegraphics[width=1\columnwidth]{images/Illinois-ratiomatch}
    \end{subfigure}%
    \caption{The 50 best matches by the proposed \emph{Fast-Match} algorithm (left) and the \emph{Ratio-Match} algorithm \cite{lowe2004sift} (right). The lines between the image pairs denote a match as proposed by the algorithm. For \emph{Fast-Match} the areas where local features were computed are marked with blue squares in the right image.}
    \label{fig:match_example}
\end{figure}

@@

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.75\columnwidth]{images/exploration}
\caption{Exploration of features based on a match. The areas shaded blue are the areas that were searched to obtain the match. The areas shaded green are candidate areas for obtaining more matches.}
\label{fig:exploration}
\end{figure}

@@

    \caption{15 objects from the 3D Objects dataset by Moreels
    and Perona \cite{moreels2007evaluation}.}
    \label{fig:3d_objects}
\end{figure}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth]{images/timings}
    \caption{Running times of different variations of \emph{Fast-Match} and \emph{Ratio-Match}. The top plot shows results for two 10~MPixel images two 3~Mpixel images is used for the comparison at the bottom. From the left, the first two results presume a precached image while the rest do not require knowing any inputs beforehand. The image pairs used be seen in Figure~\ref{fig:match_example}.}
    \label{fig:timings}
\end{figure}
